\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section \red{XXX}. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is. In addition, pressure differences acting on the interface produces a net pressure force,      
\begin{equation}
\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
\label{eq:pressure_dif} 
\end{equation}

\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids. With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension. As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.

\begin{equation}
 MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
\label{eq:MR}
\end{equation}

>>>>

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is. Pressure differences acting on the interface produces a net pressure force,      
\begin{equation}
\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
\label{eq:pressure_dif} 
\end{equation}
This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids. With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.

As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$)to that of the displaced fluid ($j$),
\begin{equation}
 \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
\label{eq:MR}
\end{equation}
MR is a function not only of fluid viscosities and saturations, but also the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
